---
title: "The impact of Basel III implementation on bank lending in South Africa"
author: "Xolani Sibande and Alistair Milne"
institute: "South African Reserve Bank"
date: "2023-05-10"
fontsize: 14
output: 
  beamer_presentation:
    toc: false
    theme: "CambridgeUS"
    colortheme: "dolphin"
    fonttheme: "structurebold"
    fig_width: 7
    fig_height: 4
    fig_caption: false
    keep_tex: true
    includes:
      in_header: preamble_beamer.tex
csl: ucl-institute-of-education-harvard.csl
bibliography: references.bib
biblio-style: sarb.bst
natbiboptions: round
aspectratio: 141
section-titles: true
---

```{r loading_packages, echo=FALSE, message=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(modelsummary)
library(plm)
library(datawizard)
library(knitr)
library(kableExtra)
library(glue)

theme <-
  theme_minimal(base_size = 6) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none",) # EU base theme
theme_set(theme) # setting ggplot theme instead of using theme function
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 500,
                      ft.arraystretch = 0.1
)

models <- read_rds(here("Outputs", "artifacts_base_model.rds"))
transition <- read_rds(here("Outputs", "artifacts_transition_model.rds"))
```

```{r funcs}
multi_line_plot <- function(data, plotname = "",
                            variables_color = 3, 
                            legend_position = "top"
                            )  {
  data %>% 
  ggplot(aes(x = Date, y = Value)) +
  geom_line(aes(color = Series, linetype = Series), size = 1) +
  theme_bw() +
    theme(
      legend.position = legend_position,
      legend.title = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.line = element_line(colour = "black"),
      panel.border = element_blank(),
      text = element_text(size = 8),
      strip.background = element_rect(colour = "white", fill = "white"),
      axis.text.x = element_text(angle = 90),
      axis.title = element_text(size = 7),
      plot.tag = element_text(size = 7)
    ) +
    labs(x = "", y = plotname) +
    scale_color_manual(values = pnw_palette("Cascades", variables_color)) 
}

source(here("Functions", "flextable_word.R"))
source(here("Functions", "modelsummary_word.R"))
source(here("Functions", "borderlines.R"))

set_flextable_defaults(
  font.size = 8,
  digits = 2,
  font.family = "Arial",
  border.color = "#537380"
)

border <-  fp_border(color = "#537380",
                     width = 1.5,
                     style = "solid")

```

## Introduction

- This paper investigates the impact of the higher regulatory capital requirements of the implementation of the Basel III in South Africa between 2013 and 2019.
- The principal data employed is monthly balance sheet data
- Focus on a small set of large banks has some advantages: business models of these banks are similar
- Our empirical specification follows previous studies of the impact of capital requirements on bank credit supply (for UK @aiyar2014international; for Peru @fang2020bank)
- We find report smaller coefficient estimates than in these previous studies or (for capital buffers) in @neryvia2023

## Literature 

- Earlier studies did not directly study the impact of regulation on bank credit
- However, found some significant effects of increased capital ratios on lending [@peek1997international; @houston1997capital] - subsidiary effect
- Some studies focus on bank which are close to the regulatory capital [@berger1994lines; @nier2005bank; @van2008welfare]
- More recently, there has been a sharper focus on regulation impact on bank lending
- @francis2012capital showed that a decline in the capital buffer resulted in risk weighted assets
- @aiyar2014international and @aiyar2016does also found a decline in bank lending in the UK which used trigger ratios
- Limited studies in emerging markets
- The best study was in Peru by @fang2020bank 

## A closer look at two related papers
\begin{itemize}
	\item Aiyar et. al. (2014):
	\begin{itemize}
		\item Minimum capital $\uparrow$ 1\%, lending , $\downarrow \approx$ 8\% 
		\item changes in requirements not (fully) anticipated
		\item no time fixed effects
	\end{itemize}
	\item Fang et. al. (2022)
	\begin{itemize}
		\item Minimum capital $\uparrow$ 1\%, lending , $\downarrow \approx$ 4\% 
		\item changes in requirements clearly flagged in advance
		\item includes time fixed effects
	\end{itemize}
\end{itemize} 


## @aiyar2014international
\centering
\includegraphics[width=\textwidth, height = 8cm]{AiyarEtAl_JMCB_2014_Table4}


##  @fang2020bank
\centering
\includegraphics[width=\textwidth, height = 8cm]{FamgEtAl_JBF_2022}

## Some reasons to be cautious
\begin{itemize}
	\item theoretical prior, changes in required bank capital RBC impact lending 
	\begin{itemize}
		\item in SR, but not LR
		\item only marginally, even in SR, when
		\begin{enumerate}
			\item banks are fully capitalised OR
			\item capital increase is flagged well in advance
		\end{enumerate}
	\end{itemize}
	\item Demand variable does not fully address endogeneity
	\begin{itemize}
		\item Aiyar at al, Minimum capital $\uparrow$, a response to unsustainable lending
		\item Fang et al, seasonal reallocation of credit
	\end{itemize}
\end{itemize}

## Seasonal reallocation of credit
\begin{itemize}
\item Composition bank credit across banks varies seasonally  
\begin{itemize}
	\item examples: Xmas, agricultural seasons
\end{itemize}
\item May be a bigger concern when 
\begin{itemize}
	\item Interventions are seasonal, as they are for Basel III 
	\item Bank customer base varies 
	\item Focusing on relative growth of bank credit (i.e. including time dummies)
\end{itemize}
\item Corrections?
\begin{itemize}
	\item Not corrected by standard demand proxy  
	\item Statistically impact should reduce using disaggregated loan categories  
	\item Or possibly correcting for demand using loan margins data
\end{itemize}
\end{itemize} 

## Developments in SA banking

- There are 34 active licensed banks in South Africa
- As of April, 2020, the \% of banking sector assets: Standard Bank of South Africa (24.1\%), First Rand (20.4\%), ABSA (19.8\%), Nedbank (17.0\%) and Investec (7.8\%); the next largest bank is Capitec (2\%)
- The ratio of bank assets to GDP is 112\% while total financial sector assets amount to 298\% of GDP
- This prudential regulation and South Africa’s well-capitalised banking sector has prevented the emergence any systemic financial crisis


## Basel III capital framework

```{r}
 basel_struc <- tibble(
   "Category" = c(
     "Basel III minima",
     "South African minima",
     "Pillar 2A",
     "South Africa base minima",
     "Pillar 2B (ICR)",
     "Prudential minima",
     "Systemically important buffer",
     "Capital conservation buffer",
     "Countercyclical buffer"
          ),
   "Percent" = c(
     "8",
     "8",
     "0.5 to 2",
     "8 + Pillar 2A",
     "no specific range",
     "8 + Pillar2A + ICR",
     "0.5 to 2.5",
     "0 to 2.5",
     "0 to 2.5")
 )

   kableExtra::kable(basel_struc, format = "latex", escape = T, booktabs = T) %>%
    kable_styling(font_size = 10, full_width = F,  position = "center") %>%
    add_header_above(header = c("Basel III capital requirement structure" = 2)) %>% 
    column_spec(column = 1, width = "10cm")
```

## Incremental implementation of capital requirments

```{r}
#| capital,
#| fig.cap = "Capital requirements. Source: South African Reserve Bank (2022). Note: RWA is risk weighted assets.",
#| cache = FALSE,
#| include = TRUE,
#| fig.height = 3

preprocessing_monthly <-  read_rds(here("Outputs", "artifacts_preprocessing_monthly.rds"))

Capital_monthly_tbl <- preprocessing_monthly$Totals$capital_buffer_tbl %>% 
  mutate(`Total capital held` = `Minimum requirement` + `Surplus capital`) %>% 
  rename(
    "Capital requirement" = `Minimum requirement`,
    "Capital buffer" = `Surplus capital`)
Capital_monthly_combined_gg <- 
  Capital_monthly_tbl %>% 
  mutate(across(.cols = -Date, .fns = ~.x/100)) %>% 
  pivot_longer(-Date, values_to = "Value", names_to = "Series") %>% 
  multi_line_plot(variables_color = 7, legend_position = "none") +
     scale_y_continuous(labels = scales::label_percent()) +
  facet_wrap(~ Series) +
  labs(y = "% of RWA")
  
Capital_monthly_combined_gg
```


## Data

- We collected data on the four major South African banks: Absa Bank, Standard Bank, First National Bank, and Nedbank
- Mainly utilised the BA900s (bank economic returns) and the BA930s (bank product lending rates)
- The Basel III capital requirements (BA700s) data was collected from the Prudential Authority 
- From the Prudential Authority, we also collected the controls data
- We focus on real economic activity lending in the BA900s is represented by lending to households and non-financial corporations. 
- However, the BA900s only report granular lending categories to households and non-financial corporations. Therefore, some aggregation was necessary.
- This aggregation essentially limited our sample to the big four lenders - not an issue

## Asset aggregation (cont.) 

```{r}
#| assets,
#| fig.cap = "Bank assets. Source: South African Reserve Bank (2022)",
#| cache = FALSE,
#| include = TRUE


preprocessing_quarterly <-  read_rds(here("Outputs", "artifacts_preprocessing_quartely.rds"))

BA_900_to_GDP_tbl <- preprocessing_quarterly$Totals$combined_gdp_ratio_data_tbl
  
BA_900_to_GDP_combined_gg <- BA_900_to_GDP_tbl %>% 
   mutate(across(.cols = -Date, .fns = ~.x/100)) %>% 
   pivot_longer(-Date, values_to = "Value", names_to = "Series") %>% 
  multi_line_plot(variables_color = 7, legend_position = "none") +
     scale_y_continuous(labels = scales::label_percent()) +
  facet_wrap(~ Series, ncol = 2, scales = "free_y") +
  labs(subtitle = "Bank assets as a percentage of GDP" )

BA_900_to_GDP_combined_gg 

```

## Methodology
Building on @fang2020bank:

$\Delta LOAN^i_{t, t-s} = \beta \Delta KR^i_{t, t-1} + \lambda \Delta KS^i_{t, t-1} + \alpha \Delta Demand^i_{t, t-1} + \gamma'  \pmb{X}^i_{t-s} + \phi^i + \tau_t + \varepsilon^i_t.$

- $\Delta LOAN^i_{t, t-s}$ is the log difference of lending 
- $\Delta KR^i_{t, t-1}$ is the bank level change in the minimum capital requirement
- $\Delta Demand^i_{t, t-1}$ is the lending demand proxy represented 
- $\pmb{X}^i_{t-s}$ is a bank level controls set at month $t-s$. 
- The fixed effects ($\phi^i$) estimate other unobserved differences in bank characteristics. 
- To account for other factors, such as changes in the macroeconomic environment, we employ time-fixed effects ($\tau_t$). 
- $\varepsilon^i_t$ using clustered standard errors

## Identification

- However, there are challenges with the identification of $\Delta KR^i_{t, t-1}$ [@fang2020bank]
- That is, it is not just the changes due to Basel III that are included in $\Delta KR^i_{t, t-1}$
- We isolate the Basel III related changes using a dummy structure (1 when there are Basel III related changes, and 0 otherwise)
- This ensures that we are estimating the Basel III impact and not other balance sheet related adjustments
- Furthermore, we use a novel approach in estimating $\Delta Demand^i_{t, t-1}$ as compared to @fang2020bank and others. However, most studies found demand effects tend to be insignificant


## Results I

```{r}

models_full_list <- list(
  household_secured_list  = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[1]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[1]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[1]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[1]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[1]]
  ),
  household_unsecured_list = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[2]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[2]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[2]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[2]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[2]]
  ),
  household_mortgage_list = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[3]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[3]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[3]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[3]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[3]]
  )
)

household_secured_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[1]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[1]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[1]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[1]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[1]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')
household_unsecured_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[2]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[2]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[2]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[2]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[2]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')
household_mortgage_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[3]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[3]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[3]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[3]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[3]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')

household_secured_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[1]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[1]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[1]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[1]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[1]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

household_unsecured_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[2]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[2]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[2]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[2]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[2]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

household_mortgage_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[3]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[3]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[3]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[3]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[3]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

household_secured_model <- 
  modelsummary_word(
  models_full_list$household_secured_list,
  coef_omit = 2:16
) 
household_unsecured_model <- 
  modelsummary_word(
  models_full_list$household_unsecured_list,
  coef_omit = 2:16
  )
household_mortgage_model <- 
  modelsummary_word(
    models_full_list$household_mortgage_list,
    coef_omit = 2:16
  )

dependant <-  c(
    "Dep. Var:\\Delta LOAN_{t, t-1}"
)
estimates <- c(
  "$\\Delta KR_{t,t-1}$",
  "",
  "$\\Delta KS_{t,t-1}$",
  "",
  "$\\Delta Demand_{t,t-1}$",
  "",
  "$ROA_{t-1}$",
  "",
  "$ROE_{t-1}$",
  "",
  "$Liquidity_{t-1}$",
  "",
  "Num.Obs.",
  "Test of equality (p-value)",
  "Adj.R squared"
)

results_table <- function(dataset = household_secured_model$body$dataset, 
                          equality_vec = household_secured_joint_test_vec, 
                          r_squared_vec = household_secured_r_squared_vec){
  table <- 
  dataset %>% 
    add_row(.after = 14,
            " " = "Test of equality (p-value)",
            "(1)" = as.character(equality_vec[1]),
            "(2)" = as.character(equality_vec[2]),
            "(3)" = as.character(equality_vec[3]),
            "(4)" = as.character(equality_vec[4]),
            "(5)" = as.character(equality_vec[5])) %>% 
       add_row(.after = 14,
            " " = "Adj.R squared",
            "(1)" = as.character(r_squared_vec[1]),
            "(2)" = as.character(r_squared_vec[2]),
            "(3)" = as.character(r_squared_vec[3]),
            "(4)" = as.character(r_squared_vec[4]),
            "(5)" = as.character(r_squared_vec[5]))
    
table[, 1] <- estimates


kableExtra::kable(table, digits = 2, format = "latex", escape = F, booktabs = T) %>%
  kable_styling(latex_options="scale_down", font_size = 10, full_width = F, position = "center") %>%
  column_spec(column = 1, width = "7cm") %>% 
  footnote(c("The dependant variables in loan growth at bank level at a monthly frequency, calculated as the log difference at t and t -1.", "Standard errors are clustered at a bank level.", "All equations include both bank and monthly effects. A test for equality p-value of < 0.1 is significant.", "*** p < 0.01, ** p < 0.05, * p < 0.1)"))
}

results_table() %>% 
  add_header_above(header = c("Household secured credit" = 6))

```


## Results II 

```{r}
results_table(household_unsecured_model$body$dataset,
              equality_vec = household_unsecured_joint_test_vec,
              r_squared_vec = household_unsecured_r_squared_vec) %>% 
    add_header_above(header = c("Household unsecured credit" = 6))

```

## Results III

```{r}

results_table(household_mortgage_model$body$dataset,
              equality_vec = household_mortgage_joint_test_vec,
              r_squared_vec = household_mortgage_r_squared_vec) %>% 
  add_header_above(header = c("Household mortgages" = 6))

```

## Results IV

```{r}

models_full_list_NFC <- list(
  corporation_secured_list  = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[4]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[4]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[4]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[4]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[4]]
  ),
  corporation_unsecured_list = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[5]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[5]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[5]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[5]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[5]]
  ),
  corporation_mortgage_list = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[6]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[6]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[6]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[6]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[6]]
  )
)

corporation_secured_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[4]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[4]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[4]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[4]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[4]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')
corporation_unsecured_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[5]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[5]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[5]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[5]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[5]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')
corporation_mortgage_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[6]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[6]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[6]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[6]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[6]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')

corporation_secured_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[4]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[4]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[4]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[4]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[4]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

corporation_unsecured_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[5]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[5]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[5]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[5]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[5]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

corporation_mortgage_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[6]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[6]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[6]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[6]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[6]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

corporation_secured_model <- 
  modelsummary_word(
  models_full_list_NFC$corporation_secured_list,
  coef_omit = 2:16
) 
corporation_unsecured_model <- 
  modelsummary_word(
  models_full_list_NFC$corporation_unsecured_list,
  coef_omit = 2:16
  )
corporation_mortgage_model <- 
  modelsummary_word(
    models_full_list_NFC$corporation_mortgage_list,
    coef_omit = 2:16
  )


results_table(corporation_secured_model$body$dataset,
              equality_vec = corporation_secured_joint_test_vec,
              r_squared_vec = corporation_secured_r_squared_vec) %>% 
    add_header_above(header = c("Non financial corporations secured credit" = 6))

```

## Results V

```{r}
results_table(corporation_unsecured_model$body$dataset,
              equality_vec = corporation_unsecured_joint_test_vec,
              r_squared_vec = corporation_unsecured_r_squared_vec) %>% 
    add_header_above(header = c("Non financial corporations unsecured credit" = 6))
```


## Results VI
```{r}
results_table(corporation_mortgage_model$body$dataset,
              equality_vec = corporation_mortgage_joint_test_vec,
              r_squared_vec = corporation_mortgage_r_squared_vec) %>% 
    add_header_above(header = c("Non financial corporations mortgage credit" = 6))
```


## Timevarying estimates via local projections [@jorda2005estimation]

```{r}
#| path,
#| fig.cap = "Impulse responses via local projections of lending ($LOAN$) to a shock in capital requirements ($KR$).",
#| cache = TRUE,
#| include = TRUE,
#| eval = TRUE

models$graphs$path_gg
```



## Conclusion I 

-  Our estimates of between 0.48 and 2.4 percentage points are lower than @fang2020bank estimates of 4 to 6 percentage points
- However, they are closer to the UK, where @aiyar2016does found 0.55 percentage points
- The SARB's gradual approach resulted in a comparably lower lending effect
- Although they focus on the impact of the surplus capital buffer on lending in South Africa, in their estimations @neryvia2023 similar magnitudes on the impact of capital requirements on lending. 
- The lower estimates are not surprising as the extent of the reduction in lending primarily depends on how expensive it is for banks to raise equity [@aiyar2016does]. South African banks, in addition, to the capital requirements, kept a significant capital buffer.

##  Conclusion II 

- The results also revealed a more significant effect on household lending versus non-financial corporation lending. 
- One explanation is that it is much easier for banks to discriminate between borrowers in their commercial business versus retail business when banks need to reduce their risk-weighted assets to meet higher capital requirements [@de2020bank]. 
- There are fewer clients on the commercial side, and the assets are larger. This higher asset base also suggests that banks are more careful or place more risk-weights on lending on the commercial than the household side [@imbierowicz2018time]. 
- In South Africa, this means that banks avoid having to pull back on lending on the commercial side as a result of higher capital requirements, with the capital buffer as a first 'shock-absorber'.
- The issue of demand effect remains a concern
- Further capital requirement endogeneity is possible in the form of anticipation effects. We address these in the paper.

## Thank You! {-}
\centering Thank You!

## References {.allowframebreaks}





