---
title: "The impact of Basel III implementation on bank lending in South Africa"
author: "Xolani Sibande and Alistair Milne"
institute: "South African Reserve Bank and Loughborough University"
date: "5 December 2023"
fontsize: 14
output: 
  beamer_presentation:
    toc: false
    theme: "CambridgeUS"
    colortheme: "dolphin"
    fonttheme: "structurebold"
    fig_width: 7
    fig_height: 4
    fig_caption: false
    keep_tex: true
    includes:
      in_header: preamble_beamer.tex
csl: ucl-institute-of-education-harvard.csl
bibliography: references.bib
biblio-style: sarb.bst
natbiboptions: round
aspectratio: 141
section-titles: false
---

```{r loading_packages, echo=FALSE, message=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(modelsummary)
library(plm)
library(datawizard)
library(knitr)
library(kableExtra)
library(glue)

theme <-
  theme_minimal(base_size = 6) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none",) # EU base theme
theme_set(theme) # setting ggplot theme instead of using theme function
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 500,
                      ft.arraystretch = 0.1
)

models <- read_rds(here("Outputs", "artifacts_base_model.rds"))
transition <- read_rds(here("Outputs", "artifacts_transition_model.rds"))
```

```{r funcs}
multi_line_plot <- function(data, plotname = "",
                            variables_color = 3, 
                            legend_position = "top"
                            )  {
  data %>% 
  ggplot(aes(x = Date, y = Value)) +
  geom_line(aes(color = Series, linetype = Series), size = 1) +
  theme_bw() +
    theme(
      legend.position = legend_position,
      legend.title = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.line = element_line(colour = "black"),
      panel.border = element_blank(),
      text = element_text(size = 8),
      strip.background = element_rect(colour = "white", fill = "white"),
      axis.text.x = element_text(angle = 90),
      axis.title = element_text(size = 7),
      plot.tag = element_text(size = 7)
    ) +
    labs(x = "", y = plotname) +
    scale_color_manual(values = pnw_palette("Cascades", variables_color)) 
}

source(here("Functions", "flextable_word.R"))
source(here("Functions", "modelsummary_word.R"))
source(here("Functions", "borderlines.R"))

set_flextable_defaults(
  font.size = 8,
  digits = 2,
  font.family = "Arial",
  border.color = "#537380"
)

border <-  fp_border(color = "#537380",
                     width = 1.5,
                     style = "solid")

```

## Introduction

- This paper investigates the impact of the higher regulatory capital requirements of the implementation of the Basel III in South Africa between 2013 and 2019.
- The principal data employed is monthly balance sheet data
- Focus on a small set of large banks has some advantages: business models of these banks are similar
- Our empirical specification follows previous studies of the impact of capital requirements on bank credit supply (for UK @aiyar2014international; for Peru @fang2020bank)
- We find little evidence of the impact of Basel III on lending

<!-- ## Literature  -->

<!-- - Earlier studies did not directly study the impact of regulation on bank credit -->
<!-- - However, found some significant effects of increased capital ratios on lending [@peek1997international; @houston1997capital] - subsidiary effect -->
<!-- - Some studies focus on bank which are close to the regulatory capital [@berger1994lines; @nier2005bank; @van2008welfare] -->
<!-- - More recently, there has been a sharper focus on regulation impact on bank lending -->
<!-- - @francis2012capital showed that a decline in the capital buffer resulted in risk weighted assets -->
<!-- - @aiyar2014international and @aiyar2016does also found a decline in bank lending in the UK which used trigger ratios -->
<!-- - Limited studies in emerging markets -->
<!-- - The best study was in Peru by @fang2020bank  -->

<!-- ## A closer look at two related papers -->
<!-- \begin{itemize} -->
<!-- 	\item Aiyar et. al. (2014): -->
<!-- 	\begin{itemize} -->
<!-- 		\item Minimum capital $\uparrow$ 1\%, lending , $\downarrow \approx$ 8\%  -->
<!-- 		\item changes in requirements not (fully) anticipated -->
<!-- 		\item no time fixed effects -->
<!-- 	\end{itemize} -->
<!-- 	\item Fang et. al. (2022) -->
<!-- 	\begin{itemize} -->
<!-- 		\item Minimum capital $\uparrow$ 1\%, lending , $\downarrow \approx$ 4\%  -->
<!-- 		\item changes in requirements clearly flagged in advance -->
<!-- 		\item includes time fixed effects -->
<!-- 	\end{itemize} -->
<!-- \end{itemize}  -->


<!-- ## @aiyar2014international -->
<!-- \centering -->
<!-- \includegraphics[width=\textwidth, height = 8cm]{AiyarEtAl_JMCB_2014_Table4} -->


<!-- ##  @fang2020bank -->
<!-- \centering -->
<!-- \includegraphics[width=\textwidth, height = 8cm]{FamgEtAl_JBF_2022} -->

<!-- ## Some reasons to be cautious -->
<!-- \begin{itemize} -->
<!-- 	\item theoretical prior, changes in required bank capital RBC impact lending  -->
<!-- 	\begin{itemize} -->
<!-- 		\item in SR, but not LR -->
<!-- 		\item only marginally, even in SR, when -->
<!-- 		\begin{enumerate} -->
<!-- 			\item banks are fully capitalised OR -->
<!-- 			\item capital increase is flagged well in advance -->
<!-- 		\end{enumerate} -->
<!-- 	\end{itemize} -->
<!-- 	\item Demand variable does not fully address endogeneity -->
<!-- 	\begin{itemize} -->
<!-- 		\item Aiyar at al, Minimum capital $\uparrow$, a response to unsustainable lending -->
<!-- 		\item Fang et al, seasonal reallocation of credit -->
<!-- 	\end{itemize} -->
<!-- \end{itemize} -->

<!-- ## Seasonal reallocation of credit -->
<!-- \begin{itemize} -->
<!-- \item Composition bank credit across banks varies seasonally   -->
<!-- \begin{itemize} -->
<!-- 	\item examples: Xmas, agricultural seasons -->
<!-- \end{itemize} -->
<!-- \item May be a bigger concern when  -->
<!-- \begin{itemize} -->
<!-- 	\item Interventions are seasonal, as they are for Basel III  -->
<!-- 	\item Bank customer base varies  -->
<!-- 	\item Focusing on relative growth of bank credit (i.e. including time dummies) -->
<!-- \end{itemize} -->
<!-- \item Corrections? -->
<!-- \begin{itemize} -->
<!-- 	\item Not corrected by standard demand proxy   -->
<!-- 	\item Statistically impact should reduce using disaggregated loan categories   -->
<!-- 	\item Or possibly correcting for demand using loan margins data -->
<!-- \end{itemize} -->
<!-- \end{itemize}  -->

<!-- ## SA banking sector -->

<!-- - There are 34 active licensed banks in South Africa -->
<!-- - As of April, 2020, the \% of banking sector assets: Standard Bank of South Africa (24.1\%), First Rand (20.4\%), ABSA (19.8\%), Nedbank (17.0\%) and Investec (7.8\%); the next largest bank is Capitec (2\%) -->
<!-- - The ratio of bank assets to GDP is 112\% -->
<!-- - This prudential regulation and South Africa’s well-capitalised banking sector has prevented the emergence any systemic financial crisis -->


<!-- ## Basel III capital framework -->

<!-- ```{r} -->
<!--  basel_struc <- tibble( -->
<!--    "Category" = c( -->
<!--      "Basel III minima", -->
<!--      "South African minima", -->
<!--      "Pillar 2A", -->
<!--      "South Africa base minima", -->
<!--      "Pillar 2B (ICR)", -->
<!--      "Prudential minima", -->
<!--      "Systemically important buffer", -->
<!--      "Capital conservation buffer", -->
<!--      "Countercyclical buffer" -->
<!--           ), -->
<!--    "Percent" = c( -->
<!--      "8", -->
<!--      "8", -->
<!--      "0.5 to 2", -->
<!--      "8 + Pillar 2A", -->
<!--      "no specific range", -->
<!--      "8 + Pillar2A + ICR", -->
<!--      "0.5 to 2.5", -->
<!--      "0 to 2.5", -->
<!--      "0 to 2.5") -->
<!--  ) -->

<!--    kableExtra::kable(basel_struc, format = "latex", escape = T, booktabs = T) %>% -->
<!--     kable_styling(font_size = 10, full_width = F,  position = "center") %>% -->
<!--     add_header_above(header = c("Basel III capital requirement structure" = 2)) %>%  -->
<!--     column_spec(column = 1, width = "10cm") -->
<!-- ``` -->

## Incremental implementation of capital requirments

```{r}
#| capital,
#| fig.cap = "Capital requirements. Source: South African Reserve Bank (2022). Note: RWA is risk weighted assets.",
#| cache = FALSE,
#| include = TRUE,
#| fig.height = 3

preprocessing_monthly <-  read_rds(here("Outputs", "artifacts_preprocessing_monthly.rds"))

Capital_monthly_tbl <- preprocessing_monthly$Totals$capital_buffer_tbl %>% 
  mutate(`Total capital held` = `Minimum requirement` + `Surplus capital`) %>% 
  rename(
    "Capital requirement" = `Minimum requirement`,
    "Capital buffer" = `Surplus capital`)
Capital_monthly_combined_gg <- 
  Capital_monthly_tbl %>% 
  mutate(across(.cols = -Date, .fns = ~.x/100)) %>% 
  pivot_longer(-Date, values_to = "Value", names_to = "Series") %>% 
  multi_line_plot(variables_color = 7, legend_position = "none") +
     scale_y_continuous(labels = scales::label_percent()) +
  facet_wrap(~ Series) +
  labs(y = "% of RWA") +
  theme(text = element_text(size = 12))
  
Capital_monthly_combined_gg
```


## Data

- We collected data on the four major South African banks: Absa Bank, Standard Bank, First National Bank, and Nedbank
- Mainly utilised the BA900s (bank economic returns) and the BA930s (bank product lending rates)
- The Basel III capital requirements (BA700s) data was collected from the Prudential Authority 
- From the Prudential Authority, we also collected the controls data
- We focus on real economic activity lending in the BA900s is represented by lending to households and non-financial corporations. 
- However, the BA900s only report granular lending categories to households and non-financial corporations. Therefore, some aggregation was necessary.
- This aggregation essentially limited our sample to the big four lenders
- Three major categories for households and non financial corporations (secured, unsecured, and mortgages)

<!-- ## Asset aggregation (cont.)  -->

```{r}
#| assets,
#| fig.cap = "Bank assets. Source: South African Reserve Bank (2022)",
#| cache = FALSE,
#| include = FALSE,
#| fig.height = 4.5,
#| fig.width = 7


preprocessing_quarterly <-  read_rds(here("Outputs", "artifacts_preprocessing_quartely.rds"))

BA_900_to_GDP_tbl <- preprocessing_quarterly$Totals$combined_gdp_ratio_data_tbl
  
BA_900_to_GDP_combined_gg <- BA_900_to_GDP_tbl %>% 
   mutate(across(.cols = -Date, .fns = ~.x/100)) %>% 
   pivot_longer(-Date, values_to = "Value", names_to = "Series") %>% 
  multi_line_plot(variables_color = 7, legend_position = "none") +
     scale_y_continuous(labels = scales::label_percent()) +
  facet_wrap(~ Series, ncol = 2, scales = "free_y") +
  labs(subtitle = "Bank assets as a percentage of GDP" ) +
  theme(text = element_text(size = 10))

BA_900_to_GDP_combined_gg 

```

## Methodology
Building on @fang2020bank:

$\Delta LOAN^i_{t, t-s} = \beta \Delta KR^i_{t, t-1} + \lambda \Delta KS^i_{t, t-1} + \alpha \Delta Demand^i_{t, t-1} + \gamma'  \pmb{X}^i_{t-s} + \phi^i + \tau_t + \varepsilon^i_t.$

- $^i$ refers to the four banks
- $\Delta LOAN^i_{t, t-s}$ is the log difference of lending 
- $\Delta KR^i_{t, t-1}$ is the change in the minimum capital requirement
- $\Delta Demand^i_{t, t-1}$ is the lending demand proxy represented 
- $\pmb{X}^i_{t-s}$ is a bank level controls set at month $t-s$. 
- The fixed effects ($\phi^i$) estimate other unobserved differences in bank characteristics. 
- To account for other factors, such as changes in the macroeconomic environment, we employ time-fixed effects ($\tau_t$). 
- $\varepsilon^i_t$ using bank clustered standard errors

<!-- ## Identification -->

<!-- - However, there are challenges with the identification of $\Delta KR^i_{t, t-1}$ [@fang2020bank] -->
<!-- - That is, it is not just the changes due to Basel III that are included in $\Delta KR^i_{t, t-1}$ -->
<!-- - We isolate the Basel III related changes using a dummy structure (1 when there are Basel III related changes, and 0 otherwise) -->
<!-- - This ensures that we are estimating the Basel III impact and not other balance sheet related adjustments -->
<!-- - Furthermore, we use a novel approach in estimating $\Delta Demand^i_{t, t-1}$ as compared to @fang2020bank and others. However, most studies found demand effects tend to be insignificant -->


## Results Household Secured Credit (Example)

```{r}

models_full_list <- list(
  household_secured_list  = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[1]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[1]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[1]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[1]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[1]]
  ),
  household_unsecured_list = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[2]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[2]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[2]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[2]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[2]]
  ),
  household_mortgage_list = list(
  models$coef_models$one_month_buffer_coeftest_model_list[[3]],
  models$coef_models$one_month_buffer_surplus_coeftest_model_list[[3]],
  models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[3]],
  models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[3]],
  models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[3]]
  )
)

household_secured_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[1]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[1]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[1]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[1]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[1]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')
household_unsecured_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[2]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[2]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[2]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[2]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[2]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')
household_mortgage_joint_test_vec <- c(
    models$joint_test$joint_test_buffer[[3]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus[[3]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand[[3]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_control[[3]]$`Pr(>F)`[2],
    models$joint_test$joint_test_buffer_surplus_demand_control[[3]]$`Pr(>F)`[2]
  ) %>% sprintf(fmt = '%#.2f')

household_secured_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[1]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[1]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[1]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[1]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[1]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

household_unsecured_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[2]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[2]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[2]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[2]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[2]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

household_mortgage_r_squared_vec <- c(
  summary(models$lm_models$one_month_buffer_ols_model_list[[3]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[3]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[3]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[3]])$adj.r.squared,
  summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[3]])$adj.r.squared
) %>% sprintf(fmt = '%#.2f')

household_secured_model <- 
  modelsummary_word(
  models_full_list$household_secured_list,
  coef_omit = 2:16
) 
household_unsecured_model <- 
  modelsummary_word(
  models_full_list$household_unsecured_list,
  coef_omit = 2:16
  )
household_mortgage_model <- 
  modelsummary_word(
    models_full_list$household_mortgage_list,
    coef_omit = 2:16
  )

dependant <-  c(
    "Dep. Var:\\Delta LOAN_{t, t-1}"
)
estimates <- c(
  "$\\Delta KR_{t,t-1}$",
  "",
  "$\\Delta KS_{t,t-1}$",
  "",
  "$\\Delta Demand_{t,t-1}$",
  "",
  "$ROA_{t-1}$",
  "",
  "$ROE_{t-1}$",
  "",
  "$Liquidity_{t-1}$",
  "",
  "Num.Obs.",
  "Test of equality (p-value)",
  "Adj.R squared"
)

results_table <- function(dataset = household_secured_model$body$dataset, 
                          equality_vec = household_secured_joint_test_vec, 
                          r_squared_vec = household_secured_r_squared_vec){
  table <- 
  dataset %>% 
    add_row(.after = 14,
            " " = "Test of equality (p-value)",
            "(1)" = as.character(equality_vec[1]),
            "(2)" = as.character(equality_vec[2]),
            "(3)" = as.character(equality_vec[3]),
            "(4)" = as.character(equality_vec[4]),
            "(5)" = as.character(equality_vec[5])) %>% 
       add_row(.after = 14,
            " " = "Adj.R squared",
            "(1)" = as.character(r_squared_vec[1]),
            "(2)" = as.character(r_squared_vec[2]),
            "(3)" = as.character(r_squared_vec[3]),
            "(4)" = as.character(r_squared_vec[4]),
            "(5)" = as.character(r_squared_vec[5]))
    
table[, 1] <- estimates


kableExtra::kable(table, digits = 2, format = "latex", escape = F, booktabs = T) %>%
  kable_styling(latex_options="scale_down", font_size = 10, full_width = F, position = "center") %>%
  column_spec(column = 1, width = "7cm") %>% 
  footnote(c("The dependant variables in loan growth at bank level at a monthly frequency, calculated as the log difference at t and t -1.", "Standard errors are clustered at a bank level.", "All equations include both bank and monthly effects. A test for equality p-value of < 0.1 is significant.", "*** p < 0.01, ** p < 0.05, * p < 0.1)"))
}

results_table() %>% 
  add_header_above(header = c("Household secured credit" = 6))

```


<!-- ## Results II  -->

<!-- ```{r} -->
<!-- results_table(household_unsecured_model$body$dataset, -->
<!--               equality_vec = household_unsecured_joint_test_vec, -->
<!--               r_squared_vec = household_unsecured_r_squared_vec) %>%  -->
<!--     add_header_above(header = c("Household unsecured credit" = 6)) -->

<!-- ``` -->

<!-- ## Results III -->

<!-- ```{r} -->

<!-- results_table(household_mortgage_model$body$dataset, -->
<!--               equality_vec = household_mortgage_joint_test_vec, -->
<!--               r_squared_vec = household_mortgage_r_squared_vec) %>%  -->
<!--   add_header_above(header = c("Household mortgages" = 6)) -->

<!-- ``` -->

<!-- ## Results IV -->

<!-- ```{r} -->

<!-- models_full_list_NFC <- list( -->
<!--   corporation_secured_list  = list( -->
<!--   models$coef_models$one_month_buffer_coeftest_model_list[[4]], -->
<!--   models$coef_models$one_month_buffer_surplus_coeftest_model_list[[4]], -->
<!--   models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[4]], -->
<!--   models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[4]], -->
<!--   models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[4]] -->
<!--   ), -->
<!--   corporation_unsecured_list = list( -->
<!--   models$coef_models$one_month_buffer_coeftest_model_list[[5]], -->
<!--   models$coef_models$one_month_buffer_surplus_coeftest_model_list[[5]], -->
<!--   models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[5]], -->
<!--   models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[5]], -->
<!--   models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[5]] -->
<!--   ), -->
<!--   corporation_mortgage_list = list( -->
<!--   models$coef_models$one_month_buffer_coeftest_model_list[[6]], -->
<!--   models$coef_models$one_month_buffer_surplus_coeftest_model_list[[6]], -->
<!--   models$coef_models$one_month_buffer_surplus_demand_coeftest_model_list[[6]], -->
<!--   models$coef_models$one_month_buffer_surplus_control_coeftest_model_list[[6]], -->
<!--   models$coef_models$one_month_buffer_surplus_demand_control_coeftest_model_list[[6]] -->
<!--   ) -->
<!-- ) -->

<!-- corporation_secured_joint_test_vec <- c( -->
<!--     models$joint_test$joint_test_buffer[[4]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus[[4]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_demand[[4]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_control[[4]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_demand_control[[4]]$`Pr(>F)`[2] -->
<!--   ) %>% sprintf(fmt = '%#.2f') -->
<!-- corporation_unsecured_joint_test_vec <- c( -->
<!--     models$joint_test$joint_test_buffer[[5]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus[[5]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_demand[[5]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_control[[5]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_demand_control[[5]]$`Pr(>F)`[2] -->
<!--   ) %>% sprintf(fmt = '%#.2f') -->
<!-- corporation_mortgage_joint_test_vec <- c( -->
<!--     models$joint_test$joint_test_buffer[[6]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus[[6]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_demand[[6]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_control[[6]]$`Pr(>F)`[2], -->
<!--     models$joint_test$joint_test_buffer_surplus_demand_control[[6]]$`Pr(>F)`[2] -->
<!--   ) %>% sprintf(fmt = '%#.2f') -->

<!-- corporation_secured_r_squared_vec <- c( -->
<!--   summary(models$lm_models$one_month_buffer_ols_model_list[[4]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[4]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[4]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[4]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[4]])$adj.r.squared -->
<!-- ) %>% sprintf(fmt = '%#.2f') -->

<!-- corporation_unsecured_r_squared_vec <- c( -->
<!--   summary(models$lm_models$one_month_buffer_ols_model_list[[5]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[5]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[5]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[5]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[5]])$adj.r.squared -->
<!-- ) %>% sprintf(fmt = '%#.2f') -->

<!-- corporation_mortgage_r_squared_vec <- c( -->
<!--   summary(models$lm_models$one_month_buffer_ols_model_list[[6]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_ols_model_list[[6]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_demand_ols_model_list[[6]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_control_ols_model_list[[6]])$adj.r.squared, -->
<!--   summary(models$lm_models$one_month_buffer_surplus_demand_control_ols_model_list[[6]])$adj.r.squared -->
<!-- ) %>% sprintf(fmt = '%#.2f') -->

<!-- corporation_secured_model <-  -->
<!--   modelsummary_word( -->
<!--   models_full_list_NFC$corporation_secured_list, -->
<!--   coef_omit = 2:16 -->
<!-- )  -->
<!-- corporation_unsecured_model <-  -->
<!--   modelsummary_word( -->
<!--   models_full_list_NFC$corporation_unsecured_list, -->
<!--   coef_omit = 2:16 -->
<!--   ) -->
<!-- corporation_mortgage_model <-  -->
<!--   modelsummary_word( -->
<!--     models_full_list_NFC$corporation_mortgage_list, -->
<!--     coef_omit = 2:16 -->
<!--   ) -->


<!-- results_table(corporation_secured_model$body$dataset, -->
<!--               equality_vec = corporation_secured_joint_test_vec, -->
<!--               r_squared_vec = corporation_secured_r_squared_vec) %>%  -->
<!--     add_header_above(header = c("Non financial corporations secured credit" = 6)) -->

<!-- ``` -->

<!-- ## Results V -->

<!-- ```{r} -->
<!-- results_table(corporation_unsecured_model$body$dataset, -->
<!--               equality_vec = corporation_unsecured_joint_test_vec, -->
<!--               r_squared_vec = corporation_unsecured_r_squared_vec) %>%  -->
<!--     add_header_above(header = c("Non financial corporations unsecured credit" = 6)) -->
<!-- ``` -->


<!-- ## Results VI -->
<!-- ```{r} -->
<!-- results_table(corporation_mortgage_model$body$dataset, -->
<!--               equality_vec = corporation_mortgage_joint_test_vec, -->
<!--               r_squared_vec = corporation_mortgage_r_squared_vec) %>%  -->
<!--     add_header_above(header = c("Non financial corporations mortgage credit" = 6)) -->
<!-- ``` -->


<!-- ## Timevarying estimates via local projections [@jorda2005estimation] -->

<!-- ```{r} -->
<!-- #| path, -->
<!-- #| fig.cap = "Impulse responses via local projections of lending ($LOAN$) to a shock in capital requirements ($KR$).", -->
<!-- #| cache = TRUE, -->
<!-- #| include = TRUE, -->
<!-- #| eval = TRUE -->

<!-- models$graphs$path_gg -->
<!-- ``` -->



<!-- ## Conclusion I  -->

<!-- -  Our estimates of between 0.48 and 2.4 percentage points are lower than @fang2020bank estimates of 4 to 6 percentage points -->
<!-- - However, they are closer to the UK, where @aiyar2016does found 0.55 percentage points -->
<!-- - The SARB's gradual approach resulted in a comparably lower lending effect -->
<!-- - Although they focus on the impact of the surplus capital buffer on lending in South Africa, in their estimations @neryvia2023 similar magnitudes on the impact of capital requirements on lending.  -->
<!-- - The lower estimates are not surprising as the extent of the reduction in lending primarily depends on how expensive it is for banks to raise equity [@aiyar2016does]. South African banks, in addition, to the capital requirements, kept a significant capital buffer. -->

##  Conclusion 

- While our set up is similar to Fang et al. (2020), we find very much weaker evidence of an impact of capital requirements on the supply of bank lending. 
- We investigate the impact three categories of lending for both household and corporate borrowers.
- Only in the case of secured credit for non-financial corporations do we obtain a statistically significant and economically sensible coefficient estimates and the coefficient is relatively small. 
- Exploring alternative dynamic estimation similarly yields little evidence of any.



<!-- ## Thank You! {-} -->
<!-- \centering Thank You! -->

## References





